Automated verification of stand-alone solar photovoltaic systems

### 2018-11-20 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
added description of the case studies
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

%------------------------------------------
\subsection{Objectives and Setup}
%------------------------------------------

@@

We performed five case studies: (a) four PV systems (700 W inverter, with 48h autonomy) deployed in four different houses in an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) situated nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); and (b) one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with 1,200 W inverter, and autonomy of just 6 h). The annual average temperature ($T$) in Manaus is from 23$^{o}$C to 32$^{o}$C; and irradiance ($G$) varies from 274 W/m$^{2}$ to 852 W/m$^{2}$ when there is sunlight (that information is provided in Lines 9 and 10 of Algorithm~\ref{alg:verification-algorithm}). Another characteristic of Manaus, based on historical data of solar irradiance, is related to the fact that only during 8 hours of the day there is PV generation, from 8:00h to 16:00h (that information is provided in Algorithm~\ref{alg:verification-algorithm} as well).

>>>>

%------------------------------------------
\subsection{Description of the Case Studies}
%------------------------------------------

We have performed five case studies to evaluate our proposed verification method: (a) four PV systems (700 W inverter, with 48h autonomy) deployed in four different houses in an indigenous community (GPS coordinates 2$^{o}$44'50.0"S 60$^{o}$25'47.8"W) situated nearby Manaus (Brazil), with each house having a different power demand (house 1 = 253 W, house 2 = 263 W, house 3 = 283 W, and house 4 = 501 W); and (b) one case concerning a system deployed as an individual system in Manaus (GPS coordinates 3$^{o}$4'20.208"S 60$^{o}$0'30.168"W), supporting 915 W of the house's load (house 5 with 1,200 W inverter, and autonomy of just 6 h).

Note that the annual average temperature ($T$) in Manaus is from 23$^{o}$C to 32$^{o}$C; and irradiance ($G$) varies from 274 W/m$^{2}$ to 852 W/m$^{2}$ when there is sunlight (that information is provided in Lines 9 and 10 of Algorithm~\ref{alg:verification-algorithm}). Another characteristic of Manaus, based on historical data of solar irradiance \textcolor{red}{Add citation here}, is related to the fact that only during 8 hours of the day there is PV generation, from 8:00h to 16:00h (that information is provided in Algorithm~\ref{alg:verification-algorithm} as well).

%------------------------------------------
\subsection{Objectives and Setup}
%------------------------------------------

@@
